### 2017-03-04 sections/implementation.tex
Update on Overleaf.

Once the matrix $\mtrx{A}$ is build for a field component the compression algorithm can be applied on it. It is purely algebraic procedure, no information about geometry of the mesh is needed.

The compression algorithm is based on low-rank approximation matrix created from SVD decomposition. The main idea that led to this implementation is the following observation. Results for time steps are not independent. They have some relation between them. List of singular values produced by the SVD method reveals the dependency between the singular vectors that form the orthogonal base of the matrix $\mtrx{A}$. \todo{Better explanation needed}

@@

where $S_{i}$ is $i$-th singular value, $U_{i}$, $V_{i}$ are corresponding singular vectors, and $n$ is the rank of the matrix $\mtrx{A}$. Considering the fact that singular values are ordered $S_{1}>S_{2}>S_{3}> ... >S_{n}$ the above formula implies that the first term would have the highest contribution and last term would have the lowest contribution to the matrix~$\mtrx{A}$. Therefore if we take only first $r$ members of the above summation we get approximation of the matrix $\mtrx{A}$

@@

But how can be the rank of approximation matrix effectively calculated from the desired approximation error? Here comes useful the interesting property of the singular values

@@

where $k=min(m, n)$, i.e. the smallest of two dimensions of the matrix $M$. The above formula states that the sum of squared elements of matrix $\mtrx{A}$ equals to the sum of squared singular values $\sigma_{i}$ of the same matrix $\mtrx{A}$. \todo{Reference to source or further explanation needed.} Using formulas \eqref{eq:svd-expansion} and \eqref{eq:svd-approx-expansion} the equation \eqref{eq:elem-sqr-sigma-sqr} can be applied to the difference between original matrix $\mtrx{A}$ and approximation matrix $A'$.

>>>>

Once the matrix $\mtrx{A}$ is built for a field component the compression algorithm can be applied on it. It is purely algebraic procedure, no information about geometry of the mesh is needed.

% The compression algorithm is based on low-rank approximation matrix created from SVD decomposition. Results for time steps are not independent. They usually have some relation between them. List of singular values produced by the SVD method reveals the dependency between the singular vectors that form the orthogonal base of the matrix $\mtrx{A}$.

@@

where $S_{i}$ is $i$-th singular value, $U_{i}$, $V_{i}$ are corresponding singular vectors, and $n$ is the rank of the matrix $\mtrx{A}$. Considering the fact that singular values are ordered $S_{1}>S_{2}>S_{3}> ... >S_{n}$ the above formula implies that the first term would have the highest contribution and last term would have the lowest contribution to the matrix~$\mtrx{A}$. Therefore if we take only first $r$ members of the above summation we get an approximation matrix

@@

But how can be the rank of approximation matrix effectively calculated from the desired approximation error? Here comes useful the interesting property of the singular values:

% TODO: Reference to source or further explanation needed. (prof. Marek?)

@@

where $k=min(m, n)$, i.e. the smallest of two dimensions of the matrix $M$. The above formula states that the sum of squared elements of matrix $\mtrx{A}$ equals to the sum of squared singular values $\sigma_{i}$ of the same matrix $\mtrx{A}$.

Using formulas \eqref{eq:svd-expansion} and \eqref{eq:svd-approx-expansion} the equation \eqref{eq:elem-sqr-sigma-sqr} can be applied to the difference between original matrix $\mtrx{A}$ and approximation matrix $A'$.

### 2017-03-04 sections/introduction.tex
Update on Overleaf.

\section{Introduction}
\label{section:introduction}

The effort to reduce size of resulting data from complex finite element analyses to accelerate (or even make possible) post-processing using common personal computer is not new. In \cite{Benes2015} is presented one possible direction for research in this area -- the replacement of discrete data produced by finite element solver by simple continuous functions. These approximation functions can be then described be low number of parameters. The focus is on \textit{geometry}. The main goal is to find the areas in domain where the output discrete function has predictable development and can be easily replaced by e.g. linear continuous function. Although this approach has great results for some class of functions it is not applicable to problem in general. For some special cases, such as functions with discontinuities, the method has poor results because approximation error is too high and -- what is more important -- it can not be controlled in advance.

In this study the purely \textit{algebraic} approach is applied. ...

\subsection{Related work}

>>>>

\section{Introduction}
\label{sec:introduction}

% Introduction to field of FEM results post-processing.

The effort to reduce size of resulting data from complex finite element analyses to accelerate (or even make possible) post-processing using common personal computer is not new.

% TODO: State of the art. Add references to work in the field of FEM results post-processing.

In \cite{Benes2016} is presented one possible direction for research in this area -- the replacement of discrete data produced by finite element solver by simple continuous functions. These approximation functions can be then described be low number of parameters. The focus is on \textit{geometry}. The main goal is to find the areas in domain where the output discrete function has predictable development and can be easily replaced by e.g. linear continuous function. Although this approach has great results for some class of functions it is not applicable to problem in general. For some special cases, such as functions with discontinuities, the method has poor results because approximation error is too high and -- what is more important -- it can not be controlled in advance.

In this study it was decided to apply purely algebraic approach. Various methods were considered, e.g. discrete wavelet transform \cite{Lui2001} and discrete cosine transform \cite{Watson1994} for their successful use in image compression. The reason why the SVD method was finally chosen is that it is well suited for all kind of data and the implementation is straightforward, considering that the results from the FEM analyses can be viewed as a series of arbitrary rectangular matrices.

% TODO: Add references to related work and related usage of SVD for compression

% TODO: Description of all terms that are used in text?
